---
title: "W_UP_01"
author: "Tiffany Alvarado"
date: "August 29, 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

I predict average number of pushups based on position   
pushups is a numerical variable, position is a categorical variable
so I use the helper file, num ~ categorical
 
# Results 

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

This boxplot shows that on average players in the skill positions do more pushups in 2 minutes than do the line players

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=mydata)
```

The numerical summary shows that skill players did about 3 times as many push ups in 2 minutes, than the line players did

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

the p-value is 0.00000941 this is less than 0.05 so I reject the $H_0$

we conclude that the skill position players can do more push ups on average than the line players

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The relationship for the variables are that whenever the line players do one push up the skill players do three times as much. So because of this the variables cause each other.  
